Something about Continuous Deductive Reasoning over Streamed RDF Data, maybe claim Soundness or some other Theoretical Quality

### 2015-06-16 content/contribution/continuous-datalog/proof-of-entailment-semantics.tex
moved Hypothesis and Lemma titles to their own lines
forced inductive step to span both columns in 2column layout mode

	\begin{hyp}\labelhyp{continuous datalog: entailment}
		For any ${CDP = \{A,S,R\} \vDash \{A',P,N\}}$, where ${CDP_{i} \vDash A' \cup E_{i}}$ for any ${i \in \mathbb{N}}$, the set of facts in a window of any range ${X \geq R}$ over the stream $P$ at a given instant ${i}$ and not in a window of any range ${Y \geq X}$ over the stream $N$ at the same instant $i$ is equal to the set of facts $E_{i}$ transitively entailed by the ${CDP}$ at that instant $i$:
		\begin{equation*}
			W^{P,X}_{i} \setminus W^{N,Y}_{i} = E_{i}
		\end{equation*}
	\end{hyp}
	In order to prove \refhyp{continuous datalog: entailment}, in which the windows over the entailed streams have a Range greater than or equal to that over the input streams, I present Lemma~\ref{hyp:continuous datalog: entailment lemma} as the general case where the windows have an arbitrary range.
	\begin{lem}\label{hyp:continuous datalog: entailment lemma}
		For any ${CDP \vDash \{A',P,N\}}$, where ${CDP_{i} \vDash A' \cup E_{i}}$ for any ${i \in \mathbb{N}}$, the set of facts in a window of any range ${X \in \mathbb{N}}$ over the stream $P$ at a given instant ${i}$ and not in a window of any range ${Y \geq X}$ over the stream $N$ at the same instant $i$ is equal to the set of transient entailments at that instant $i$ less the intersection of all previous sets of transient entailments from instant ${i-1}$ up to and including ${i-X}$:
		\begin{equation*}
			W^{P,X}_{i} \setminus W^{N,Y}_{i} = E_{i} \setminus \mathop{\cap}^{X}_{d=1} E_{i-d}
		\end{equation*}
	\end{lem}

@@

		\begin{figure}[p]

@@

		\end{figure}

>>>>

	\begin{hyp}\labelhyp{continuous datalog: entailment} \hfill \\
		For any ${CDP = \{A,S,R\} \vDash \{A',P,N\}}$, where ${CDP_{i} \vDash A' \cup E_{i}}$ for any ${i \in \mathbb{N}}$, the set of facts in a window of any range ${X \geq R}$ over the stream $P$ at a given instant ${i}$ and not in a window of any range ${Y \geq X}$ over the stream $N$ at the same instant $i$ is equal to the set of facts $E_{i}$ transitively entailed by the ${CDP}$ at that instant $i$:
		\begin{equation*}
			W^{P,X}_{i} \setminus W^{N,Y}_{i} = E_{i}
		\end{equation*}
	\end{hyp}
	In order to prove \refhyp{continuous datalog: entailment}, in which the windows over the entailed streams have a Range greater than or equal to that over the input streams, I present Lemma~\ref{hyp:continuous datalog: entailment lemma} as the general case where the windows have an arbitrary range.
	\begin{lem}\label{hyp:continuous datalog: entailment lemma} \hfill \\
		For any ${CDP \vDash \{A',P,N\}}$, where ${CDP_{i} \vDash A' \cup E_{i}}$ for any ${i \in \mathbb{N}}$, the set of facts in a window of any range ${X \in \mathbb{N}}$ over the stream $P$ at a given instant ${i}$ and not in a window of any range ${Y \geq X}$ over the stream $N$ at the same instant $i$ is equal to the set of transient entailments at that instant $i$ less the intersection of all previous sets of transient entailments from instant ${i-1}$ up to and including ${i-X}$:
		\begin{equation*}
			W^{P,X}_{i} \setminus W^{N,Y}_{i} = E_{i} \setminus \mathop{\cap}^{X}_{d=1} E_{i-d}
		\end{equation*}
	\end{lem}

@@

		\begin{figure*}[p]

@@

		\end{figure*}
